Methods and Results

### 2025-10-14 methods_results.qmd
methods/results finished, need to fix descriptives table and equations to docx

---
title: "Methods and Results"
format: docx
bibliography: 
  mylibrary.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(kableExtra)
library(tidybayes)

@@

The main model for mean REE with $\textrm{cond}$ representing the condition (either control or PCOS) was as follows:
$$
\begin{align*}
\hat{\theta}_{ijkl} &\sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl}) \\[6pt]

\mu_{ijkl} &= \beta_0 + \beta_1\,\text{cond}_[ijkl]
       + \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond}
       + \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond}
       + \alpha_{0,\mathrm{arm}[k]}
       + \alpha_{0,\mathrm{effect}[l]} \\[10pt]

\begin{pmatrix}
\alpha_{0,\mathrm{lab}[i]} \\[4pt]
\alpha_{1,\mathrm{lab}[i]}
\end{pmatrix}
&\sim 
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{lab}}
\right),
\quad
\Sigma_{\mathrm{lab}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} \\[4pt]
\rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}}
\end{pmatrix}

\text{, for lab i = 1,} \dots \text{,I} \\[12pt]

\begin{pmatrix}
\alpha_{0,\mathrm{study}[j]} \\[4pt]
\alpha_{1,\mathrm{study}[j]}
\end{pmatrix}
&\sim 
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{study}}
\right),
\quad
\Sigma_{\mathrm{study}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} \\[4pt]
\rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}}
\end{pmatrix} 
\text{, for study j = 1,} \dots \text{,J} \\[12pt]

\alpha_{0,\mathrm{arm}[k]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}}) 
\text{, for arm k = 1,} \dots \text{,K} \\[12pt]
\alpha_{0,\mathrm{effect}[l]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}}) 
\text{, for effect l = 1,} \dots \text{,L} \\[12pt]

\end{align*}
$$

@@

$$
\begin{align*}
\beta_0 &\sim \text{Student-}t(3,\, 1441.81,\, 84.56) \\[4pt]
\beta_1 &\sim \text{Student-}t(3,\, 0,\, 200) \\[12pt]

\sigma^2_{0,\mathrm{study}} &\sim \text{Half-student-}t(3,\, 149.89,\, 82.91) \\[4pt]
\sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\, 
\sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}}, \sigma^2_{0,\mathrm{effect}} &\sim \text{Half-student-}t(3,\, 0,\, 112.4) \\[12pt]

\mathrm{corr}_{\mathrm{lab}} &\sim \mathrm{LKJ}(1) \\[4pt]
\mathrm{corr}_{\mathrm{study}} &\sim \mathrm{LKJ}(1)
\end{align*}
$$

@@

$$
\begin{align*}
\log(\hat{\theta}_{ijkl}) &\sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl}) \\[6pt]

\mu_{ijkl} &= \beta_0 + \beta_1\,\text{cond}_{[ijkl]} 
       + \beta_2\,\tilde{m}_{[ijkl]}
       + \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond}
       + \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond}
       + \alpha_{0,\mathrm{arm}[k]}
       + \alpha_{0,\mathrm{effect}[l]} \\[8pt]

m &= \log(y_{i,\mathrm{mean,[ijkl]}}) \\[3pt]
\tilde{m} &\sim \mathcal{N}(m,\, \sigma_{\log(y_{i,\mathrm{mean,[ijkl]}})}^2) \\[10pt]

\begin{pmatrix}
\alpha_{0,\mathrm{lab}[i]} \\[4pt]
\alpha_{1,\mathrm{lab}[i]}
\end{pmatrix}
&\sim 
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{lab}}
\right),
\quad
\Sigma_{\mathrm{lab}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} \\[4pt]
\rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}}
\end{pmatrix}

\text{, for lab i = 1,} \dots \text{,I} \\[12pt]

\begin{pmatrix}
\alpha_{0,\mathrm{study}[j]} \\[4pt]
\alpha_{1,\mathrm{study}[j]}
\end{pmatrix}
&\sim 
\mathcal{N}\!\left(
\begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix},
\Sigma_{\mathrm{study}}
\right),
\quad
\Sigma_{\mathrm{study}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} \\[4pt]
\rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}}
\end{pmatrix} 
\text{, for study j = 1,} \dots \text{,J} \\[12pt]

\alpha_{0,\mathrm{arm}[k]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}}) 
\text{, for arm k = 1,} \dots \text{,K} \\[12pt]
\alpha_{0,\mathrm{effect}[l]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}}) 
\text{, for effect l = 1,} \dots \text{,L} \\[12pt]
\end{align*}
$$
where $\log(\hat{\theta}_{ijkl})$ is the $l\textrm{th}$ natural logarithm of the standard deviation of REE estimate from the $k\textrm{th}$ arm, for the $j\textrm{th}$ study, conducted by the $i\textrm{th}$ lab and $\sigma^2_{ijkl}$ is the corresponding sampling error for that estimate. The random intercepts for the $i\textrm{th}$ lab, $j\textrm{th}$ study, $k\textrm{th}$ arm, and $l\textrm{th}$ standard deviation of REE estimate are $\alpha_{0,lab[i]}$, $\alpha_{0,study[j]}$, $\alpha_{0,arm[k]}$, and $\alpha_{0,effect[l]}$ respectively each with standard deviation of $\sigma^2_{0,lab[i]}$, $\sigma^2_{0,study[j]}$, $\sigma^2_{0,arm[k]}$, and $\sigma^2_{0,effect[l]}$. The parameter $\beta_0$ represents the fixed effect estimate of standard deviation of REE for control conditions and $\beta_1$ the fixed effect estimate for the offset from this for the PCOS conditions (i.e., the difference between conditions). The estimated offset was allowed to vary across both labs and studies each reflected by $\alpha_{1,lab[i]}$ and $\alpha_{1,study[j]}$ respectively, and these effects were also modelled as correlated with the corresponding random intercepts with covariance $\Sigma_{lab}$ and $\Sigma_{study}$, and $\mathrm{corr}_{\mathrm{lab}}$ and $\mathrm{corr}_{\mathrm{study}}$ correlation matrices. Finally, $\beta_{2}$ represents the fixed effect of the natural logarithm of the corresponding mean REE estimate $\tilde{m}$ which is modelled as estimated with measurement error i.e., $m$ represents the point estimate for the $l\textrm{th}$ natural logarithm of the mean REE estimate from the $k\textrm{th}$ arm, for the $j\textrm{th}$ study, conducted by the $i\textrm{th}$ lab and $\sigma_{\log(y_{i,\mathrm{mean,[ijkl]}})}^2$ is the corresponding sampling error for that estimate.

The priors for this model were as follows:
$$
\begin{align*}
\beta_0 &\sim \text{Student-}t(3,\, 5.54,\, 0.80) \\[4pt]
\beta_1 &\sim \text{Student-}t(3,\, 0,\, 5.3) \\[4pt]
\beta_2 &\sim \text{Student-}t(3,\, 0,\, 2.5) \\[12pt]

\text{mean}(\tilde{m}) &\sim \text{Half-student-}t(3,\, 7.28,\, 0.62) \\[4pt]
\text{sd}(\tilde{m}) &\sim \text{Half-student-}t(3,\, 0,\, 5) \\[12pt]

\sigma^2_{0,\mathrm{study}} &\sim \text{Half-student-}t(3,\, 1.08,\, 1.06) \\[4pt]
\sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\, 
\sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}}, \sigma^2_{0,\mathrm{effect}} &\sim \text{Half-student-}t(3,\, 0,\, 2.5) \\[12pt]

\mathrm{corr}_{\mathrm{lab}} &\sim \mathrm{LKJ}(1) \\[4pt]
\mathrm{corr}_{\mathrm{study}} &\sim \mathrm{LKJ}(1)
\end{align*}

$$
where the prior for $\beta_{0}$, which corresponded to the model intercept and standard deviation of REE in the control condition, was again set based on meta-analysis of the standard deviation of REEs for women from two large studies of healthy people [@velasquezUseAmmoniaInhalants2011; @pavlidouRevisedHarrisBenedict2023] though set with a conservative degrees of freedom for the $\textrm{Student-}t$ distribution.The random intercept $\sigma^2_{0,study}$ was set similarly to this. The prior for the fixed effect $\beta_{1}$, reflecting the difference between control and PCOS conditions was set based on a wide range of possible values. Given that in many cases of variables in the field there is an approximate relationship of ~1 for the natural logarithm of the standard deviation conditioned upon the natural logarithm of the mean [@steeleMetaanalysisVariationSport2023a] we set this prior to reflect the range of differences on the on the log scale (i.e., $\log(1584)$). We then set a prior that permits values approximately across this range of values with the majority of it's mass centred around zero. The prior for the fixed effect $\beta_{2}$, reflecting the relationship between the natural logarithm of the mean REE with the natural logarithm of the standard deviation of REE, was set it to be weakly informative centred on zero with a wide scale to indicate uncertainty in this outcome specifically despite the typical relationship close to ~1. Priors for the measurement error of the natural logarithm of the mean REE estimate $\tilde{m}$ were again based upon meta-analysis of the aforementioned studies, though measurement error has to be positive, as does the corresponding standard deviation of this error, so we set these to conservative wide $\textrm{half-student-}t$ distributions. The remaining random effects were set based on the default weakly regularising priors for `brms` and scaled to the expected response values using a $\textrm{half-student-}t$ distribution with 3 degrees of freedom and $\mu=0$, and both correlation matrices $\textrm{corr}_{lab}$ and $\textrm{corr}_{study}$ were set with an $\textrm{LKJcorr(1)}$ distribution.

@@

$$
\begin{align*}
\hat{\theta}_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma^2_{ij}) \\[6pt]

\mu_{ij} &= \beta_0
       + \alpha_{0,\mathrm{lab}[i]}
       + \alpha_{0,\mathrm{study}[j]} \\[10pt]

\alpha_{0,\mathrm{lab}[i]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{lab}}) 
\text{, for lab i = 1,} \dots \text{,I} \\[12pt]
\alpha_{0,\mathrm{study}[j]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{study}}) 
\text{, for study j = 1,} \dots \text{,J} \\[12pt]

\end{align*}
$$

>>>>

---
title: "Methods and Results"
format: docx
bibliography: 
  mylibrary.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)

@@

The main model for mean REE with $\textrm{cond}$ representing the condition (either control or PCOS) was as follows:
<!-- $$ -->
<!-- \begin{align*} -->
<!-- \hat{\theta}_{ijkl} &\sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl}) \\[6pt] -->

<!-- \mu_{ijkl} &= \beta_0 + \beta_1\,\text{cond}_[ijkl] -->
<!--        + \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond} -->
<!--        + \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond} -->
<!--        + \alpha_{0,\mathrm{arm}[k]} -->
<!--        + \alpha_{0,\mathrm{effect}[l]} \\[10pt] -->

<!-- \begin{pmatrix} -->
<!-- \alpha_{0,\mathrm{lab}[i]} \\[4pt] -->
<!-- \alpha_{1,\mathrm{lab}[i]} -->
<!-- \end{pmatrix} -->
<!-- &\sim  -->
<!-- \mathcal{N}\!\left( -->
<!-- \begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix}, -->
<!-- \Sigma_{\mathrm{lab}} -->
<!-- \right), -->
<!-- \quad -->
<!-- \Sigma_{\mathrm{lab}} = -->
<!-- \begin{pmatrix} -->
<!-- \sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} \\[4pt] -->
<!-- \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}} -->
<!-- \end{pmatrix}  -->

<!-- \text{, for lab i = 1,} \dots \text{,I} \\[12pt] -->

<!-- \begin{pmatrix} -->
<!-- \alpha_{0,\mathrm{study}[j]} \\[4pt] -->
<!-- \alpha_{1,\mathrm{study}[j]} -->
<!-- \end{pmatrix} -->
<!-- &\sim  -->
<!-- \mathcal{N}\!\left( -->
<!-- \begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix}, -->
<!-- \Sigma_{\mathrm{study}} -->
<!-- \right), -->
<!-- \quad -->
<!-- \Sigma_{\mathrm{study}} = -->
<!-- \begin{pmatrix} -->
<!-- \sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} \\[4pt] -->
<!-- \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}} -->
<!-- \end{pmatrix}  -->
<!-- \text{, for study j = 1,} \dots \text{,J} \\[12pt] -->

<!-- \alpha_{0,\mathrm{arm}[k]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}})  -->
<!-- \text{, for arm k = 1,} \dots \text{,K} \\[12pt] -->
<!-- \alpha_{0,\mathrm{effect}[l]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}})  -->
<!-- \text{, for effect l = 1,} \dots \text{,L} \\[12pt] -->

<!-- \end{align*} -->
<!-- $$ -->

$$
\hat{\theta}_{ijkl} \sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl})
$$

$$
\mu_{ijkl} = \beta_0 + \beta_1\,\text{cond}_{ijkl} 
+ \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond} 
+ \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond} 
+ \alpha_{0,\mathrm{arm}[k]} + \alpha_{0,\mathrm{effect}[l]}
$$

$$
\begin{pmatrix}
\alpha_{0,\mathrm{lab}[i]} \\
\alpha_{1,\mathrm{lab}[i]}
\end{pmatrix}
\sim 
\mathcal{N}\Bigg(
\begin{pmatrix} 0 \\ 0 \end{pmatrix},
\Sigma_{\mathrm{lab}}
\Bigg), 
\quad
\Sigma_{\mathrm{lab}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}} \sigma_{0,\mathrm{lab}} \sigma_{1,\mathrm{lab}} \\
\rho_{\mathrm{lab}} \sigma_{0,\mathrm{lab}} \sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}}
\end{pmatrix},
\text{ for lab } i = 1, \dots, I
$$

$$
\begin{pmatrix}
\alpha_{0,\mathrm{study}[j]} \\
\alpha_{1,\mathrm{study}[j]}
\end{pmatrix}
\sim 
\mathcal{N}\Bigg(
\begin{pmatrix} 0 \\ 0 \end{pmatrix},
\Sigma_{\mathrm{study}}
\Bigg), 
\quad
\Sigma_{\mathrm{study}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}} \sigma_{0,\mathrm{study}} \sigma_{1,\mathrm{study}} \\
\rho_{\mathrm{study}} \sigma_{0,\mathrm{study}} \sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}}
\end{pmatrix},
\text{ for study } j = 1, \dots, J
$$

$$
\alpha_{0,\mathrm{arm}[k]} \sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}}), 
\text{ for arm } k = 1, \dots, K
$$

$$
\alpha_{0,\mathrm{effect}[l]} \sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}}), 
\text{ for effect } l = 1, \dots, L
$$

@@

<!-- $$ -->
<!-- \begin{align*} -->
<!-- \beta_0 &\sim \text{Student-}t(3,\, 1441.81,\, 84.56) \\[4pt] -->
<!-- \beta_1 &\sim \text{Student-}t(3,\, 0,\, 200) \\[12pt] -->

<!-- \sigma^2_{0,\mathrm{study}} &\sim \text{Half-student-}t(3,\, 149.89,\, 82.91) \\[4pt] -->
<!-- \sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\,  -->
<!-- \sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}}, \sigma^2_{0,\mathrm{effect}} &\sim \text{Half-student-}t(3,\, 0,\, 112.4) \\[12pt] -->

<!-- \mathrm{corr}_{\mathrm{lab}} &\sim \mathrm{LKJ}(1) \\[4pt] -->
<!-- \mathrm{corr}_{\mathrm{study}} &\sim \mathrm{LKJ}(1) -->
<!-- \end{align*} -->
<!-- $$ -->

$$
\beta_0 \sim \text{Student-}t(3, 1441.81, 84.56) \\
\beta_1 \sim \text{Student-}t(3, 0, 200)
$$

$$
\sigma^2_{0,\mathrm{study}} \sim \text{Half-student-}t(3, 149.89, 82.91) \\
\sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\, 
\sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}},\, \sigma^2_{0,\mathrm{effect}} \sim \text{Half-student-}t(3, 0, 112.4)
$$

$$
\mathrm{corr}_{\mathrm{lab}} \sim \mathrm{LKJ}(1) \\
\mathrm{corr}_{\mathrm{study}} \sim \mathrm{LKJ}(1)
$$

@@

<!-- $$ -->
<!-- \begin{align*} -->
<!-- \log(\hat{\theta}_{ijkl}) &\sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl}) \\[6pt] -->

<!-- \mu_{ijkl} &= \beta_0 + \beta_1\,\text{cond}_{[ijkl]}  -->
<!--        + \beta_2\,\tilde{m}_{[ijkl]} -->
<!--        + \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond} -->
<!--        + \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond} -->
<!--        + \alpha_{0,\mathrm{arm}[k]} -->
<!--        + \alpha_{0,\mathrm{effect}[l]} \\[8pt] -->

<!-- m &= \log(y_{i,\mathrm{mean,[ijkl]}}) \\[3pt] -->
<!-- \tilde{m} &\sim \mathcal{N}(m,\, \sigma_{\log(y_{i,\mathrm{mean,[ijkl]}})}^2) \\[10pt] -->

<!-- \begin{pmatrix} -->
<!-- \alpha_{0,\mathrm{lab}[i]} \\[4pt] -->
<!-- \alpha_{1,\mathrm{lab}[i]} -->
<!-- \end{pmatrix} -->
<!-- &\sim  -->
<!-- \mathcal{N}\!\left( -->
<!-- \begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix}, -->
<!-- \Sigma_{\mathrm{lab}} -->
<!-- \right), -->
<!-- \quad -->
<!-- \Sigma_{\mathrm{lab}} = -->
<!-- \begin{pmatrix} -->
<!-- \sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} \\[4pt] -->
<!-- \rho_{\mathrm{lab}}\,\sigma_{0,\mathrm{lab}}\,\sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}} -->
<!-- \end{pmatrix}  -->

<!-- \text{, for lab i = 1,} \dots \text{,I} \\[12pt] -->

<!-- \begin{pmatrix} -->
<!-- \alpha_{0,\mathrm{study}[j]} \\[4pt] -->
<!-- \alpha_{1,\mathrm{study}[j]} -->
<!-- \end{pmatrix} -->
<!-- &\sim  -->
<!-- \mathcal{N}\!\left( -->
<!-- \begin{pmatrix} 0 \\[4pt] 0 \end{pmatrix}, -->
<!-- \Sigma_{\mathrm{study}} -->
<!-- \right), -->
<!-- \quad -->
<!-- \Sigma_{\mathrm{study}} = -->
<!-- \begin{pmatrix} -->
<!-- \sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} \\[4pt] -->
<!-- \rho_{\mathrm{study}}\,\sigma_{0,\mathrm{study}}\,\sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}} -->
<!-- \end{pmatrix}  -->
<!-- \text{, for study j = 1,} \dots \text{,J} \\[12pt] -->

<!-- \alpha_{0,\mathrm{arm}[k]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}})  -->
<!-- \text{, for arm k = 1,} \dots \text{,K} \\[12pt] -->
<!-- \alpha_{0,\mathrm{effect}[l]} &\sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}})  -->
<!-- \text{, for effect l = 1,} \dots \text{,L} \\[12pt] -->
<!-- \end{align*} -->
<!-- $$ -->

$$
\log(\hat{\theta}_{ijkl}) \sim \mathcal{N}(\mu_{ijkl}, \sigma^2_{ijkl})
$$

$$
\mu_{ijkl} = \beta_0 + \beta_1\,\text{cond}_{[ijkl]} 
+ \beta_2\,\tilde{m}_{[ijkl]}
+ \alpha_{0,\mathrm{lab}[i]} + \alpha_{1,\mathrm{lab}[i]}\,\text{cond} 
+ \alpha_{0,\mathrm{study}[j]} + \alpha_{1,\mathrm{study}[j]}\,\text{cond} 
+ \alpha_{0,\mathrm{arm}[k]} + \alpha_{0,\mathrm{effect}[l]}
$$

$$
m = \log(y_{i,\mathrm{mean,[ijkl]}})
$$

$$
\tilde{m} \sim \mathcal{N}(m, \sigma_{\log(y_{i,\mathrm{mean,[ijkl]}})}^2)
$$

$$
\begin{pmatrix}
\alpha_{0,\mathrm{lab}[i]} \\
\alpha_{1,\mathrm{lab}[i]}
\end{pmatrix}
\sim 
\mathcal{N}\Bigg(
\begin{pmatrix} 0 \\ 0 \end{pmatrix},
\Sigma_{\mathrm{lab}}
\Bigg),
\quad
\Sigma_{\mathrm{lab}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{lab}} & \rho_{\mathrm{lab}} \sigma_{0,\mathrm{lab}} \sigma_{1,\mathrm{lab}} \\
\rho_{\mathrm{lab}} \sigma_{0,\mathrm{lab}} \sigma_{1,\mathrm{lab}} & \sigma^2_{1,\mathrm{lab}}
\end{pmatrix},
\text{ for lab } i = 1, \dots, I
$$

$$
\begin{pmatrix}
\alpha_{0,\mathrm{study}[j]} \\
\alpha_{1,\mathrm{study}[j]}
\end{pmatrix}
\sim 
\mathcal{N}\Bigg(
\begin{pmatrix} 0 \\ 0 \end{pmatrix},
\Sigma_{\mathrm{study}}
\Bigg),
\quad
\Sigma_{\mathrm{study}} =
\begin{pmatrix}
\sigma^2_{0,\mathrm{study}} & \rho_{\mathrm{study}} \sigma_{0,\mathrm{study}} \sigma_{1,\mathrm{study}} \\
\rho_{\mathrm{study}} \sigma_{0,\mathrm{study}} \sigma_{1,\mathrm{study}} & \sigma^2_{1,\mathrm{study}}
\end{pmatrix},
\text{ for study } j = 1, \dots, J
$$

$$
\alpha_{0,\mathrm{arm}[k]} \sim \mathcal{N}(0, \sigma^2_{0,\mathrm{arm}}), 
\text{ for arm } k = 1, \dots, K
$$

$$
\alpha_{0,\mathrm{effect}[l]} \sim \mathcal{N}(0, \sigma^2_{0,\mathrm{effect}}), 
\text{ for effect } l = 1, \dots, L
$$

where $\log(\hat{\theta}_{ijkl})$ is the $l\textrm{th}$ natural logarithm of the standard deviation of REE estimate from the $k\textrm{th}$ arm, for the $j\textrm{th}$ study, conducted by the $i\textrm{th}$ lab and $\sigma^2_{ijkl}$ is the corresponding sampling error for that estimate. The random intercepts for the $i\textrm{th}$ lab, $j\textrm{th}$ study, $k\textrm{th}$ arm, and $l\textrm{th}$ standard deviation of REE estimate are $\alpha_{0,lab[i]}$, $\alpha_{0,study[j]}$, $\alpha_{0,arm[k]}$, and $\alpha_{0,effect[l]}$ respectively each with standard deviation of $\sigma^2_{0,lab[i]}$, $\sigma^2_{0,study[j]}$, $\sigma^2_{0,arm[k]}$, and $\sigma^2_{0,effect[l]}$. The parameter $\beta_0$ represents the fixed effect estimate of standard deviation of REE for control conditions and $\beta_1$ the fixed effect estimate for the offset from this for the PCOS conditions (i.e., the difference between conditions). The estimated offset was allowed to vary across both labs and studies each reflected by $\alpha_{1,lab[i]}$ and $\alpha_{1,study[j]}$ respectively, and these effects were also modelled as correlated with the corresponding random intercepts with covariance $\Sigma_{lab}$ and $\Sigma_{study}$, and $\mathrm{corr}_{\mathrm{lab}}$ and $\mathrm{corr}_{\mathrm{study}}$ correlation matrices. Finally, $\beta_{2}$ represents the fixed effect of the natural logarithm of the corresponding mean REE estimate $\tilde{m}$ which is modelled as estimated with measurement error i.e., $m$ represents the point estimate for the $l\textrm{th}$ natural logarithm of the mean REE estimate from the $k\textrm{th}$ arm, for the $j\textrm{th}$ study, conducted by the $i\textrm{th}$ lab and $\sigma_{\log(y_{i,\mathrm{mean,[ijkl]}})}^2$ is the corresponding sampling error for that estimate.

The priors for this model were as follows:
<!-- $$ -->
<!-- \begin{align*} -->
<!-- \beta_0 &\sim \text{Student-}t(3,\, 5.54,\, 0.80) \\[4pt] -->
<!-- \beta_1 &\sim \text{Student-}t(3,\, 0,\, 5.3) \\[4pt] -->
<!-- \beta_2 &\sim \text{Student-}t(3,\, 0,\, 2.5) \\[12pt] -->

<!-- \text{mean}(\tilde{m}) &\sim \text{Half-student-}t(3,\, 7.28,\, 0.62) \\[4pt] -->
<!-- \text{sd}(\tilde{m}) &\sim \text{Half-student-}t(3,\, 0,\, 5) \\[12pt] -->

<!-- \sigma^2_{0,\mathrm{study}} &\sim \text{Half-student-}t(3,\, 1.08,\, 1.06) \\[4pt] -->
<!-- \sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\, -->
<!-- \sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}}, \sigma^2_{0,\mathrm{effect}} &\sim \text{Half-student-}t(3,\, 0,\, 2.5) \\[12pt] -->

<!-- \mathrm{corr}_{\mathrm{lab}} &\sim \mathrm{LKJ}(1) \\[4pt] -->
<!-- \mathrm{corr}_{\mathrm{study}} &\sim \mathrm{LKJ}(1) -->
<!-- \end{align*} -->

<!-- $$ -->

$$
\beta_0 \sim \text{Student-}t(3, 5.54, 0.80) \\
\beta_1 \sim \text{Student-}t(3, 0, 5.3) \\
\beta_2 \sim \text{Student-}t(3, 0, 2.5)
$$

$$
\text{mean}(\tilde{m}) \sim \text{Half-student-}t(3, 7.28, 0.62) \\
\text{sd}(\tilde{m}) \sim \text{Half-student-}t(3, 0, 5)
$$

$$
\sigma^2_{0,\mathrm{study}} \sim \text{Half-student-}t(3, 1.08, 1.06) \\
\sigma^2_{0,\mathrm{lab}},\, \sigma^2_{1,\mathrm{lab}},\, 
\sigma^2_{1,\mathrm{study}},\, \sigma^2_{0,\mathrm{arm}},\, \sigma^2_{0,\mathrm{effect}} 
\sim \text{Half-student-}t(3, 0, 2.5)
$$

$$
\mathrm{corr}_{\mathrm{lab}} \sim \mathrm{LKJ}(1) \\
\mathrm{corr}_{\mathrm{study}} \sim \mathrm{LKJ}(1)
$$

where the prior for $\beta_{0}$, which corresponded to the model intercept and standard deviation of REE in the control condition, was again set based on meta-analysis of the standard deviation of REEs for women from two large studies of healthy people [@velasquezUseAmmoniaInhalants2011; @pavlidouRevisedHarrisBenedict2023] though set with a conservative degrees of freedom for the $\textrm{Student-}t$ distribution.The random intercept $\sigma^2_{0,study}$ was set similarly to this. The prior for the fixed effect $\beta_{1}$, reflecting the difference between control and PCOS conditions was set based on a wide range of possible values. Given that in many cases of variables in the field there is an approximate relationship of ~1 for the natural logarithm of the standard deviation conditioned upon the natural logarithm of the mean [@steeleMetaanalysisVariationSport2023a] we set this prior to reflect the range of differences on the on the log scale (i.e., $\log(1584)$). We then set a prior that permits values approximately across this range of values with the majority of it's mass centred around zero. The prior for the fixed effect $\beta_{2}$, reflecting the relationship between the natural logarithm of the mean REE with the natural logarithm of the standard deviation of REE, was set it to be weakly informative centred on zero with a wide scale to indicate uncertainty in this outcome specifically despite the typical relationship close to ~1. Priors for the measurement error of the natural logarithm of the mean REE estimate $\tilde{m}$ were again based upon meta-analysis of the aforementioned studies, though measurement error has to be positive, as does the corresponding standard deviation of this error, so we set these to conservative wide $\textrm{half-student-}t$ distributions. The remaining random effects were set based on the default weakly regularising priors for `brms` and scaled to the expected response values using a $\textrm{half-student-}t$ distribution with 3 degrees of freedom and $\mu=0$, and both correlation matrices $\textrm{corr}_{lab}$ and $\textrm{corr}_{study}$ were set with an $\textrm{LKJcorr(1)}$ distribution.

@@

<!-- $$ -->
<!-- \begin{align*} -->
<!-- \hat{\theta}_{ij} &\sim \mathcal{N}(\mu_{ij}, \sigma^2_{ij}) \\[6pt] -->

<!-- \mu_{ij} &= \beta_0 -->
<!--        + \alpha_{0,\mathrm{lab}[i]} -->
<!--        + \alpha_{0,\mathrm{study}[j]} \\[10pt] -->
